Privacy-Preserving Localisation Using Private Linear-Combination Aggregation

### 2020-11-06 main.tex
Another change of template ... not for the Transactions on Automatic Control (template not found so very default IEEEtran used) Updated template folder with the latest IEEEtran files

%% bare_jrnl_compsoc.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% Computer Society journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

\documentclass[10pt,journal,compsoc]{IEEEtran}

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\else
  \usepackage[dvips]{graphicx}
\fi

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs

\author{Marko~Ristic,
        Benjamin~Noack,~\IEEEmembership{Member,~IEEE,}
        and~Uwe~D.~Hanebeck,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Ristic, B. Noack and U. D. Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: marko.ristic@kit.edu}% <-this % stops an unwanted space
}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localisation protocols, thus not preserving participants’ data privacy. Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common non-linear measurement model applications and forfeit broad applicability. We define the novel notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Information Filter with range-sensor measurements. Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and is implemented and run on simulations to evaluate its accuracy and performance. The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where nodes are not trusted or data is considered sensitive.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
State Estimation, Data Privacy, Sensor Fusion, Kalman Filters.
\end{IEEEkeywords}}

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
% Computer Society journal (but not conference!) papers do something unusual
% with the very first section heading (almost always called "Introduction").
% They place it ABOVE the main text! IEEEtran.cls does not automatically do
% this for you, but you can achieve this effect with the provided
% \IEEEraisesectionheading{} command. Note the need to keep any \label that
% is to refer to the section immediately after \section in the above as
% \IEEEraisesectionheading puts \section within a raised box.

\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}. Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}. Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy. These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally. Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain. With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}. For example, an aircraft localisation scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles. Or in autonomous vehicle state estimation, benefit from neighbouring vehicles' information may be desired while no participant wishes to share information about their hardware. Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations. All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data. Our contributions in this work will be presented in two parts. We first propose a novel aggregation-based encryption scheme which allows private aggregation of weighted sums, before we develop a localisation filter using this scheme such that sensor and navigator privacy is preserved.

@@

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
% 
%        d8888 8888888b.  8888888b.  8888888888 888b    888 8888888b. 8888888 Y88b   d88P 
%       d88888 888   Y88b 888   Y88b 888        8888b   888 888  "Y88b  888    Y88b d88P  
%      d88P888 888    888 888    888 888        88888b  888 888    888  888     Y88o88P   
%     d88P 888 888   d88P 888   d88P 8888888    888Y88b 888 888    888  888      Y888P    
%    d88P  888 8888888P"  8888888P"  888        888 Y88b888 888    888  888      d888b    
%   d88P   888 888        888        888        888  Y88888 888    888  888     d88888b   
%  d8888888888 888        888        888        888   Y8888 888  .d88P  888    d88P Y88b  
% d88P     888 888        888        8888888888 888    Y888 8888888P" 8888888 d88P   Y88b 
%                                                                                         
%                                                                                         
%                                                                                         
%

\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
\end{LaTeXdescription}

@@

% use section* for acknowledgement
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

>>>>

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

\documentclass[10pt,letterpaper,oneside,twocolumn,journal]{IEEEtran}

@@

\begin{document}
%
% paper title
\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation}
%
%
% author names and IEEE memberships
\author{Marko~Ristic,
        Benjamin~Noack,~\IEEEmembership{Member,~IEEE,}
        and~Uwe~D.~Hanebeck,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
\thanks{M. Ristic, B. Noack and U. D. Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany. e-mail: marko.ristic@kit.edu}}% <-this % stops a space
% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

% The paper headers
% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localisation protocols, thus not preserving participants’ data privacy. Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common non-linear measurement model applications and forfeit broad applicability. We define the novel notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Information Filter with range-sensor measurements. Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and is implemented and run on simulations to evaluate its accuracy and performance. The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where nodes are not trusted or data is considered sensitive.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
State Estimation, Data Privacy, Sensor Fusion, Kalman Filters.
\end{IEEEkeywords}

% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

\section{Introduction}
\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}. Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}. Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy. These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally. Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain. With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}. For example, an aircraft localisation scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles. Or in autonomous vehicle state estimation, benefit from neighbouring vehicles' information may be desired while no participant wishes to share information about their hardware. Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations. All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data. Our contributions in this work will be presented in two parts. We first propose a novel aggregation-based encryption scheme which allows private aggregation of weighted sums, before we develop a localisation filter using this scheme such that sensor and navigator privacy is preserved.

@@

% 
%        d8888 8888888b.  8888888b.  8888888888 888b    888 8888888b. 8888888 Y88b   d88P 
%       d88888 888   Y88b 888   Y88b 888        8888b   888 888  "Y88b  888    Y88b d88P  
%      d88P888 888    888 888    888 888        88888b  888 888    888  888     Y88o88P   
%     d88P 888 888   d88P 888   d88P 8888888    888Y88b 888 888    888  888      Y888P    
%    d88P  888 8888888P"  8888888P"  888        888 Y88b888 888    888  888      d888b    
%   d88P   888 888        888        888        888  Y88888 888    888  888     d88888b   
%  d8888888888 888        888        888        888   Y8888 888  .d88P  888    d88P Y88b  
% d88P     888 888        888        8888888888 888    Y888 8888888P" 8888888 d88P   Y88b 
%                                                                                         
%                                                                                         
%                                                                                         
%

\appendices
\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
\end{LaTeXdescription}

@@

% use section* for acknowledgment
\section*{Acknowledgment}
